Papers

### 2025-06-24 papers.qmd
update and add link to file

- Calalo JA., Ngo TT., Sullivan SR., Strand K., Buggeln JH., Lokesh R., Roth AM., Carter MJ., Kurtzer IL., & Cashaback JGA. (2024). Online movements reflect ongoing deliberation. *bioR$\chi$iv*. ---
[{{< ai doi >}}](https://doi.org/10.1101/2024.08.19.608669){target="_blank" style="color: inherit;"}

@@

## In Press

- Sullivan SR., Lokesh R., Peters CS., Calalo J., Roth AR., Buggeln JH., Ngo TT., Carter MJ., & Cashaback JGA. (In Press). Indecision under time pressure arises from suboptimal switching behaviour. *Journal of Neurophysiology*. ---
[{{< ai doi >}}](https://doi.org/10.1152/jn.00563.2024){target="_blank" style="color: inherit;"}

@@

>>>>

@@

## Accepted or In Press

- Calalo JA, Ngo T, Sullivan S, Roth A, Lokesh R, Buggeln JH, Strand K, Marchhart V, Carter MJ, Kurtzer I, & Cashaback JGA. (Accepted). Online movements reflect ongoing deliberation. *Journal of Neuroscience*.

@@

- Sullivan SR., Lokesh R., Peters CS., Calalo J., Roth AR., Buggeln JH., Ngo TT., Carter MJ., & Cashaback JGA. (2025). Indecision under time pressure arises from suboptimal switching behaviour. *Journal of Neurophysiology*. ---
[{{< ai doi >}}](https://doi.org/10.1152/jn.00563.2024){target="_blank" style="color: inherit;"}
[{{< fa file-pdf >}}](https://raw.github.com/cartermaclab/carterlab-papers/main/2025_sullivan-etal_indecision-under-time-pressure-arises-from-suboptimal-switching-behavior.pdf){target="_blank" style="color: inherit;"}
